\appendix
\section{Appendix - Interview guide for a Platoon test driver}

This interview guide contains wide spectrum of questions regarding truck platooning and platooning in general. Interviewee is a platoon test driver, which is very fortunate for our research reasons. We are concentrating on higher level platoon architecture and communication, meaning all participants of V2V and V2I communication, although insights from potential user(driver) who already has experience with platooning might give us different angle to look at the problem.\par
% 
General questions about platooning and its implementation:
\begin{itemize}[noitemsep]
    \item Please tell us about research/development you are part of. What are the goals of whole study?
    \item How does the setup/architecture of platoon in your case looks like? Fully or partial automated? How many trucks (minimum-maximum numbers)?
    \item What limitations/requirements does your project contains? Only highways? EU roads or worldwide? 
    \item What are the reasons of those limitations/requirements? Technology? Law? People are not ready to accept platooning?
    \item As an inside man maybe you can predict when and to what level platooning will be implemented on the roads? \\
    %
    \item As a test driver please elaborate on what are critical and maybe unexpected findings after researching and testing platooning on the roads?
    \item What advantages and disadvantages platooning brings to truck drivers? Do drivers feel positively about upcoming technologies?
\end{itemize}
%
\par
%
More in depth technical questions:
\begin{itemize}[noitemsep]
    \item What kinds of communication your project includes? V2V, V2I? Is it dependant on road infrastructure?
    \item What types of technologies are used for V2V? Why?
    \item What are the main concerns regarding vehicle to vehicle communication?
    \item What types of technologies used for V2I (if used)? Why?
    \item Main concerns for vehicle to infrastructure communication?
\end{itemize}