\section{Literature review}\label{sec:literature}
% 
% Introduction to literature review
% 
We can overally conclude that concept of platooning is a heavily researched area. The articles regarding vehicles driving in strings, range as back as the eighties \cite{Peppard1974StringSystems}.
Since then the research has been divided into two major areas, as described by \cite{Vinel2015Vehicle-to-vehicleScenarios}. First area is the \emph{Cooperative adaptive cruise control} and the second one is \emph{platooning}. While both touch the scope of our project and should be researched, we focused mainly on the latter one.\par
% 
In this chapter we review some of the most recent and most significant works. Two of them are SARTRE \cite{Chan2012ProjectSARTRE} and Safespot \cite{Safespot}, both supported by the European Commission. Then chapter continues by discussing the inter-vehicular connectivity and Companion \cite{2016CompanionProject} project afterwards.\par
% 
At the end of the chapter, examples of other works are shown, to describe some of the challenges researched in connection with Platooning.

\input{04LiteratureReview/sartreReview}

\input{04LiteratureReview/Safespot}

\input{04LiteratureReview/VehicularNetworks}

\input{04LiteratureReview/Companion}

\input{04LiteratureReview/platooningEnergySavings}

\input{04LiteratureReview/other}

\subsection{Conclusion}
% Write summary of literature review
The key findings in this chapter, besides the fact that there is a lot of research material about the subject, are:
\begin{itemize}[noitemsep]
    \item There are systems developed, where Cooperative Adaptive Cruise Control (crucial part of platooning) has been successfully tried out and tested. Most of the vehicles used GPS, some kind of wireless communication and a radar to determine distance from vehicles in front.
    \item There are fuel savings, while platooning, for all vehicles - both leading and following vehicles. These savings depend on distance of the vehicles and slope of the road.
    \item Different models can be used for controlling the operation of the platoon, from the perspective of fuel savings and usability (how vehicles join platoons, how two platoons can merge).
\end{itemize}
% 
We have reviewed some of the most significant works concerning platooning, including comprehensive EU-founded projects like SARTRE or Companion. As the research progressed, we kept finding more and more material of great informational value, ranging from detailed technical challenges of the standards used in vehicular environments to broader aspects of platooning. Naturally, not all of them can be listed in this chapter and/or reviewed in great detail. Material listed here, however, gives a good picture of the state of the art within the field up to date. Our focus for the next part of this report will be put on determining the stakeholders and their requirements for the platooning concept.\par
