\section{Technology}\label{sec:technology}

Usually, during platooning vehicles are moving with high speeds and therefore can only be connected for a short period of time. Furthermore, due to the high mobility, the neighbouring vehicles may change very often. The connections need to be established locally and with as little set-up time, as possible, otherwise we risk two vehicles being out of range. In this chapter we explore local wireless networks, that are crucial for enabling any platooning scenario. First we see, what \acrshort{VANET} is and what is its relation to Vehicle-to-Vehicle and Vehicle-to-Infrastructure communication. Then we will investigate into the standards that are prevalent in establishing these connections, such as 802.11 or \acrshort{arib} T109. We will cover the basics of the operation of these technologies, as well as their relative performance in platooning scenarios.\par
% 
At the end, we will shortly describe \acrshort{GPS}, as this technology is a requirement in many cases of platooning implementation.

\input{08Technology/VANET}

\input{08Technology/V2I}

\input{08Technology/V2V}

\input{08Technology/GPS}

\subsection{Conclusion}

We can see that authorities are aware of the need for inter-vehicular communication. Developed standards and allocated frequency bands indicate the readiness for the platooning scenario. Although the standards are still very recent and it may take a while, before all the issues are resolved (e.g. quality of service issues during higher node penetration in \acrshort{wave} \& \acrshort{ETSI} ITS-G5), generally, there is technology capable of transmitting any data required for the platooning to be enabled. There are some differences among regions of world, for instance the \acrshort{arib} vs. 802.11p standards, which use different protocols and different frequencies. These differences, however are mostly present on the \acrshort{PHY} and \acrshort{MAC} layer, thus a uniform solution can be developed on the higher layers, if 802.11p, ITS-G5 or \acrshort{arib} is used. \acrshort{wave} architecture even contains standards and guidelines for the communication at network and transport layer, thus allowing for even easier adoption of platooning.