\section{Empirical data}\label{sec:data}
% 
In this section we gather all the relevant empirical data from projects, research papers, interviews and surveys that we have introduced in earlier chapters. First, an interview with \acrfull{dtl} test truck driver of platooning is presented. Followed by secondary data section where data about fuel saving, drag, latency and monetised benefits of platooning are shown. The last section presents results from several surveys, filled  by truck drivers and fleet operators. It shows general opinion about platooning from on of the main stakeholders' perspective.
% 
\subsection{Interviews}
% 
Early in the process we have contacted several stakeholders like Car2car communication consortium, Scania, Vejdirektoratet (Danish road Authority) and Morten Lindbo, press officer of \acrshort{dtl} by email. We only got one response from Morten Lindbo, who gave us contacts to their technical consultant and test driver - Finn Bjerremand, with whom we managed to have a Skype interview.
% 
\input{06EmpiricalData/FinnBjerremandInterview}
% 
\subsection{Secondary data}
% 
To prove that platooning is not just another technology being developed without a real added value, several projects and researches has been made to obtain the data to prove its benefits (some of them are mentioned in Literature review chapter - \hyperref[sec:SARTRE]{\acrshort{sartre}}, \hyperref[sec:Companion]{Companion}). As we didn't have sufficient budget and time to do the whole development of the system and later on to carry out test to get the data, we looked into those projects to find out whether platooning will be beneficial business perspective. The areas we tried to cover are fuel consumption, drag, latency, and monetising.
% 
\input{06EmpiricalData/fuel-savings}
% 
\input{06EmpiricalData/money-benefits}
% 
\input{06EmpiricalData/latency}
% 
\input{06EmpiricalData/surveys}
% 
\subsection{Conclusion}
All the research made about state of the art would be worthless if we could not prove our grounds with facts and tested data. The main findings from this chapter include:
% 
\begin{itemize}[noitemsep]
    \item The platooning would increase the safety of driving. It would also lower the load on the drivers.
    \item The trucks save fuel while platooning. These savings are dependant on:
    \begin{itemize}[noitemsep,nolistsep]
        \item Distance between trucks. (The smaller the distance, the higher fuel savings).
        \item Lateral offset of the vehicles. (The higher offset, the smaller savings).
    \end{itemize}
    \item Latency may be influenced by density of traffic in different day times.
    \item The perceptions of platooning among industry professionals is rather mixed, although it likely that a group of 'early adopters' could be established without problems.
\end{itemize}
% 
Results gathered from various experiments will help us elicit the requirements and analyse possible solutions in following chapters.